Titeln på avhandlingens språk

### 2023-02-16 body/part1/overview/methodology.tex
wca case

\medskip
We proceed to demonstrate the practical utility of our methodology as applied to \gls{WCA} by setting up a series of scenarios.
We deployed a \emph{Gabriel}-powered~\cite{chen2018application} \gls{WCA} application on a small testbed consisting of
\begin{inlineenum}
    \item a server computer acting as a cloudlet
    \item a 802.11n Wi-Fi \gls{AP} connected to the cloudlet via ethernet
    \item \num{10} Android smartphones connected wirelessly to the \gls{AP}, emulating users for the application
\end{inlineenum}.
Three scenarios were considered, corresponding to setups under ideal network conditions with \num{1} and \num{10} clients, plus an additional scenario with \num{10} clients located at a distance from the \gls{AP} such that the signal strength was significantly degraded.
Each scenario was repeated a \num{100} times for statistical validity.
These setups already showcase the flexibility of our approach.

\todo[inline]{Finish?}

>>>>

\medskip
We proceed to demonstrate the practical utility of our methodology as applied to \gls{WCA} by setting up a series of scenarios.
We deployed a \emph{Gabriel}-powered~\cite{chen2018application} \gls{WCA} application on a small testbed consisting of
\begin{inlineenum}
    \item a server computer acting as a cloudlet
    \item a 802.11n Wi-Fi \gls{AP} connected to the cloudlet via ethernet
    \item \num{10} Android smartphones connected wirelessly to the \gls{AP}, emulating users for the application
\end{inlineenum}.
Three scenarios were considered, corresponding to setups under ideal network conditions with \num{1} and \num{10} clients, plus an additional scenario with \num{10} clients located at a distance from the \gls{AP} such that the signal strength was significantly degraded.
Each scenario was repeated a \num{100} times for statistical validity.

\begin{figure}
    \begin{subfigure}[t]{.45\textwidth}
        \centering%
        \includegraphics[width=\textwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/rtt_fb_vs_nofb}%
        \caption{
            Comparison of round-trip-times for inputs that triggered a state transition in the task model versus inputs that did not.
        }\label{fig:wca:rtt}%
    \end{subfigure}%
    \hfill%
    \begin{subfigure}[t]{.45\textwidth}
        \centering%
        \includegraphics[width=\textwidth]{publications/2019EdgeDroid/plots/comparison/nofonts/box_feedback}%
        \caption{%
            Distribution of latency across system components for inputs that triggered a state transition in the task model.
        }\label{fig:wca:latency}
    \end{subfigure}%
    \caption{
        Example results from the \acs{WCA} case study.
        Figures originally published in \cref{paper:olguinmunoz2019edgedroid}.
    }
\end{figure}

These setups already showcase the flexibility of our approach.
Our trace-based implementation of the methodology allows for detailed measurements of system performance at different levels, from individual components to specific task steps.
This provides valuable insights into the bottlenecks and areas for optimization in the system.
We find, for example, that \glspl{RTT} for feedback-rich inputs are up to an order of magnitude greater than feedback-less inputs\footnote{%
    In this context, \emph{feedback-rich} inputs refer to inputs which trigger a transition in step in the internal task model of the application and thus cause the generation of feedback which is then provided to the user.
    Conversely, \emph{feedback-less} inputs are inputs which are silently discarded at the backend and do not generated noticeable feedback.
}; see \cref{fig:wca:rtt}.
The flexibility of the methodology also allows researchers to zoom into specific components or steps of the system to gain deeper insights, which can inform the design and development of future systems.
For example, the results in \cref{fig:wca:latency} suggest that improving the quality of the wireless link should be a priority for scaling the application.
The system scales linearly with respect to the number of clients, but the impaired Wi-Fi greatly affects the performance of feedback-rich inputs, with delays sometimes exceeding the threshold for acceptable user experience.

Overall, the study demonstrates the usefulness of the trace-based methodology in evaluating system performance.
The results also underscore the need for optimization of system components and the importance of network quality in delivering a satisfactory user experience.
